Project

### 2022-04-02 Project/DraftR.Rmd
Update DraftR.Rmd

```{r}
#select all rows that contains season info except for winter and columns related
clim.not.win <- subset(clim.ca, subset = year %in% c("year 2011", "year 2012", "year 2013"),
                   select=-c(d.snowpack, Dec.FebTav, wTmin))
head(clim.not.win)
```
## Visualize Climate Similarity/Disimilarity

@@

@@

@@

Do plants transplanted from low-, mid-, and high- ranges vary in their ability to phenologically adapt to ranges outside their native range?

@@

>>>>

```{r}
ggplot(clim.win, aes(x = year, y = d.snowpack, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Winter 2010 - 2014") +
  ylab("Days with Snowpack") +
  theme_classic()
```

```{r}
#select all rows that contains season info except for winter and columns related
clim.not.win <- subset(clim.ca, subset = year %in% c("year 2011", "year 2012", "year 2013"),
                   select=-c(d.snowpack, Dec.FebTav, wTmin))
head(clim.not.win)
```
```{r}
ggplot(clim.not.win, aes(x = year, y = avmaxminTJuly, color = ID)) +
  geom_point(size = 0.8, alpha = 0.8) +
  geom_line(aes(group = ID), color = "grey", size = 0.3, alpha = 0.5) +
  xlab("Year 2011 - 2013") +
  ylab("Mean July temperature (ºC)") +
  theme_classic()
```

## Visualize Climate Similarity/Disimilarity

@@

```{r}
clim.win$tr.si.yr <- paste(clim.win$ID, clim.win$year)
row.names(clim.win) <- clim.win$tr.si.yr
clim.win <- subset(clim.win, select = -c(ID, year) )
head(clim.win)
```

@@

```{r}
clim.not.win$tr.si.yr <- paste(clim.not.win$ID, clim.not.win$year)
row.names(clim.not.win) <- clim.not.win$tr.si.yr
clim.not.win <- subset(clim.not.win, select = -c(ID, year) )
head(clim.not.win)
```

@@

@@

head(phendat)
```
